---
title: 'R code for "Gendered multilingualism in highland Daghestan: story of a loss"'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.width = 9)
library(tidyverse)

options(scipen=999)
theme_set(theme_bw())

df <- read_csv("https://raw.githubusercontent.com/LingConLab/2018_suplementary_for_Gendered_multilingualism_in_highland_Daghestan_story_of_a_loss/master/data.csv")
```

## Figure 2.
Knowledge of Kumyk among men in Chuni for the whole time period (percent of all men)

```{r}
df %>% 
  filter(sex == "m",
         residence == "Chuni",
         year_of_birth_dec > 1900,
         year_of_birth_dec < 2000,
         str_detect(language, "Kumyk")) %>% 
  group_by(year_of_birth_dec, distance) %>% 
  count(knowledge) %>% 
  spread(knowledge, n, fill = 0) %>% 
  mutate(knowledge = round(`1`/(`1`+`0`)*100),
         number_of_people = `1`+`0`) %>% 
  ggplot(aes(year_of_birth_dec, knowledge))+
  geom_col()+
  scale_x_continuous(breaks = c(189:200*10),
                     labels = paste0(c(189:200*10), "s"))+
  scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"),
                     limits = c(0, 100))+
  labs(y = "", x = "")+
  scale_fill_grey() ->
  p_2
ggsave(p_2, filename = "Fig_2.eps", device = "eps")
```

## Figure 3. 
Knowledge of Russian among men and women in Chuni over the whole period

```{r}
df %>% 
  filter(residence == "Chuni",
         year_of_birth_dec > 1900,
         str_detect(language, "Russian")) %>% 
  group_by(year_of_birth_dec, sex) %>% 
  summarise(knowledge_n = sum(knowledge),
            number_of_people = n(),
            knowledge = knowledge_n/number_of_people*100) %>% 
  ggplot(aes(year_of_birth_dec, knowledge, fill = sex))+
  geom_col(position = "dodge")+
  scale_x_continuous(breaks = c(189:200*10),
                     labels = paste0(c(189:200*10), "s"))+
  scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"),
                     limits = c(0, 100))+
  labs(y = "", x = "")+
  scale_fill_grey()+
  theme(legend.title = element_blank())->
  p_3
ggsave(p_3, filename = "Fig_3.eps", device = "eps")
```

## Figure 4. 
Knowledge of Tsudakhar and (or) Akusha among men and women in Chuni over the whole period

```{r}
df %>% 
   filter(residence == "Chuni",
          year_of_birth_dec > 1900,
          year_of_birth_dec < 2000,
          str_detect(language, "Tsudakhar|Dargwa")) %>% 
  spread(language, knowledge) %>% 
  mutate(lang_knowledge = ifelse(Tsudakhar == 1, 1, ifelse(Dargwa == 1, 1, 0))) %>% 
   group_by(year_of_birth_dec, sex) %>% 
   mutate(lang_knowledge = sum(lang_knowledge)/n()*100,
          number_of_people = n()) %>%
   select(sex, year_of_birth_dec, lang_knowledge, number_of_people) %>% 
   ggplot(aes(year_of_birth_dec, lang_knowledge, fill = sex,
              label = paste0(round(lang_knowledge, 2), "%")))+
   geom_col(position = "dodge")+
   labs(y = "", x = "")+
   scale_fill_grey()+
   scale_x_continuous(breaks = c(189:200*10),
                     labels = paste0(c(189:200*10), "s"))+
   scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"),
                     limits = c(0, 100))+
  geom_hline(yintercept = 100, linetype = 3)+
    theme(legend.title = element_blank())->
  p_4
ggsave(p_4, filename = "Fig_4.eps", device = "eps")
```


## Figure 5. 
The number of languages spoken by men and women in highland Daghestan

```{r}
df %>% 
  group_by(index, residence) %>% 
  mutate(knowledge = sum(knowledge)) %>% 
  ggplot(aes(`year of birth`, factor(knowledge)), shape = 20)+
  geom_point()+
  facet_wrap(~sex)+
  labs(y = "", x = "")+
  theme(strip.background = element_blank(),
        strip.placement = "outside",
        legend.title=element_blank(),
        axis.ticks = element_blank())->
  p_5
ggsave(p_5, filename = "Fig_5.eps", device = "eps")
```

## Figure 6. 
Knowledge of distant languages in Daghestan for the whole time period

```{r}
df %>%
  filter(str_detect(distance, "distant")) %>%
  group_by(index, residence) %>% 
  mutate(n_knowledge = sum(knowledge)) %>%
  select(index, residence, year_of_birth_dec, sex, n_knowledge) %>% 
  distinct() %>% 
  group_by(year_of_birth_dec, sex) %>% 
  mutate(number_of_people = n()) %>% 
  group_by(year_of_birth_dec, sex, n_knowledge, number_of_people) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(r_knowledge = n/(number_of_people)*100,
         n_knowledge = factor(n_knowledge),
         year_of_birth_dec_s = paste0(year_of_birth_dec, "s")) %>%
  ggplot(aes(sex, r_knowledge, fill = n_knowledge))+
  geom_col(position = position_stack(reverse = T))+
  labs(y = "", x = "")+
  scale_fill_grey()+
  scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"))+
  facet_wrap(~year_of_birth_dec_s, strip.position = "bottom", nrow = 1)+
  theme(panel.spacing =unit(.1, "lines"),
        panel.border = element_blank(), 
        strip.background = element_blank(),
        strip.placement = "outside",
        legend.title=element_blank(),
        axis.ticks = element_blank())->
  p_6
ggsave(p_6, filename = "Fig_6.eps", device = "eps")
```



## Figure 7. 
Knowledge of Russian among men and women in Daghestan for the whole time period

```{r}
df %>%
  filter(str_detect(distance, "distant|Russian")) %>% 
  group_by(index, residence, distance) %>% 
  mutate(n_knowledge = if_else(sum(knowledge) > 0, 1, 0)) %>% 
  distinct(index, residence, year_of_birth_dec, distance, n_knowledge) %>%
  group_by(year_of_birth_dec, distance) %>% 
  summarise(lang_knowledge = (sum(n_knowledge))/n()*100) %>% 
  ggplot(aes(year_of_birth_dec, lang_knowledge, fill = distance))+
  geom_col(position = "dodge")+
  labs(y = "", x = "")+
  scale_fill_grey()+
  scale_x_continuous(breaks = c(189:200*10),
                     labels = paste0(c(189:200*10), "s"))+
  scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"),
                     limits = c(0, 100))+
  geom_hline(yintercept = 100, linetype = 3)+
  theme(legend.title = element_blank())->
  p_7
ggsave(p_7, filename = "Fig_7.eps", device = "eps")
```

## Figure 8. 
Knowledge of Russian and distant languages among men in Daghestan for the whole time period

```{r}
df %>%
  filter(str_detect(distance, "distant|Russian"),
         sex == "m") %>% 
  group_by(index, residence, distance) %>% 
  mutate(n_knowledge = if_else(sum(knowledge) > 0, 1, 0)) %>% 
  distinct(index, residence, year_of_birth_dec, distance, n_knowledge) %>%
  group_by(year_of_birth_dec, distance) %>% 
  summarise(lang_knowledge = (sum(n_knowledge))/n()*100) %>% 
  ggplot(aes(year_of_birth_dec, lang_knowledge, fill = distance))+
  geom_col(position = "dodge")+
  labs(y = "", x = "")+
  scale_fill_grey()+
  scale_x_continuous(breaks = c(189:200*10),
                     labels = paste0(c(189:200*10), "s"))+
  scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"),
                     limits = c(0, 100))+
  geom_hline(yintercept = 100, linetype = 3)+
  theme(legend.title = element_blank())->
  p_8
ggsave(p_8, filename = "Fig_8.eps", device = "eps")
```


## Figure 9. 
Knowledge of neighbouring languages in Daghestan among men and women for the whole time period


```{r}
df %>%
  filter(str_detect(distance, "neighbouring")) %>%
  group_by(index, residence) %>%
  mutate(n_knowledge = sum(knowledge)) %>%
  group_by(year_of_birth_dec, sex) %>% 
  mutate(number_of_people = n()) %>% 
  count(year_of_birth_dec, sex, n_knowledge, number_of_people) %>%
  ungroup() %>% 
  mutate(r_knowledge = n/number_of_people*100,
         n_knowledge = factor(n_knowledge),
         year_of_birth_dec_s = paste0(year_of_birth_dec, "s")) %>% 
  ggplot(aes(sex, r_knowledge, fill = n_knowledge))+
  geom_col(position = position_stack(reverse = T))+
  labs(y = "", x = "")+
  scale_fill_grey()+
  scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"))+
  facet_wrap(~year_of_birth_dec_s, strip.position = "bottom", nrow = 1)+
  theme(panel.spacing=unit(.1, "lines"),
        panel.border = element_blank(), 
        strip.background = element_blank(),
        strip.placement = "outside",
        legend.title=element_blank(),
        axis.ticks = element_blank())->
  p_9
ggsave(p_9, filename = "Fig_9.eps", device = "eps")
```



## Figure 10.
Knowledge of at least one neighbouring language in Daghestan among men and women for the whole time period 

```{r}
df %>%
  filter(str_detect(distance, "neighbour"),
         language != "Russian") %>% 
  group_by(index, residence, sex) %>% 
  mutate(n_knowledge = if_else(sum(knowledge) > 0, 1, 0)) %>% 
  distinct(index, residence, sex, year_of_birth_dec, n_knowledge) %>% 
  group_by(year_of_birth_dec, sex) %>%
  mutate(lang_knowledge = sum(n_knowledge)/n()*100,
         number_of_people = n()) %>%
  ggplot(aes(year_of_birth_dec, lang_knowledge, fill = sex))+
  geom_col(position = "dodge")+
  labs(y = "", x = "")+
  scale_fill_grey()+
  scale_x_continuous(breaks = c(189:200*10),
                     labels = paste0(c(189:200*10), "s"))+
  scale_y_continuous(breaks = 0:5*20,
                     labels = paste0(c(0:5*20), "%"),
                     limits = c(0, 100))+
  theme(legend.title = element_blank())->
  p_10
ggsave(p_10, filename = "Fig_10.eps", device = "eps")
```
